Isomorphic Interpreters from Logically Reversible Abstract Machines

### 2012-03-02 iso-int/rc-iso-int.tex
abstract

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
\end{abstract}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  In our previous work [RC'11, POPL'12], we developed a reversible
  programming language and established that every computation in it is a
  (partial) isomorphism that is reversible and that preserves
  information. The language is founded on type isomorphisms that have a clear
  categorical semantics but that are awkward as a notation for writing actual
  programs, especially recursive programs. This paper remedies this aspect by
  presenting a systematic technique for developing a large and expressive
  class of reversible recursive programs, that of logically reversible
  small-step abstract machines. In other words, this paper shows that once we
  have a logically reversible machine in a notation of our choice, expressing
  the machine as an isomorphic interpreter can be done systematically and
  does not present any significant conceptual difficulties. Concretely, we
  develop several simple interpreters over numbers and addition, move on to
  tree traversals, and finish with a meta-circular interpreter for our
  reversible language. Generally, this gives us a means of developing large
  reversible programs with the ease of reasoning at the level of a
  conventional small-step semantics.
\end{abstract}
